### 2020-10-02 readme.Rmd
updating the package name

[![Travis build status](https://travis-ci.com/skiptoniam/qrbp.svg?branch=master)](https://travis-ci.com/skiptoniam/qrbp)

[![Codecov test coverage](https://codecov.io/gh/skiptoniam/qrbp/branch/master/graph/badge.svg)](https://codecov.io/gh/skiptoniam/qrbp?branch=master)

## qrbp is temporary R package that will be ingested into [ecomix](https://github.com/skiptoniam/ecomix) for generating quasi random background points for multiple species Poisson point process models.

>>>>

[![Travis build status](https://travis-ci.com/skiptoniam/ppmData.svg?branch=master)](https://travis-ci.com/skiptoniam/ppmData)

[![Codecov test coverage](https://codecov.io/gh/skiptoniam/ppmData/branch/master/graph/badge.svg)](https://codecov.io/gh/skiptoniam/ppmData?branch=master)

## ppmData is temporary R package that will be ingested into [ecomix](https://github.com/skiptoniam/ecomix) for generating quasi random background points for multiple species Poisson point process models.
